% LaTeX file for resume
% This file uses the resume document class (res.cls)

\documentclass{friggeri-cv}
\usepackage{enumerate}
\usepackage{url}
\usepackage{graphicx}
\usepackage{wrapfig}
\setlength{\textheight}{9.5in}  % increase text height to fit on 1-page

\begin{document}
\header{yu-ching}{lin}{research leader}

%----------------------
%  basic information
%----------------------
\begin{aside}
\section{contact}
	0921895172
    \href{mailto:vagante@gmail.com}{vagante@gmail.com}
    \href{http://tw.linkedin.com/pub/yu-ching-lin/43/737/913/}{my linkedin}
    \href{http://mpac.ee.ntu.edu.tw/~vagante}{http://mpac.ee.ntu.edu.tw/~vagante}

\section{programming}
    C, Java, Python
    Matlab, Hadoop
    Shell Script
\end{aside}

%----------------------
%  education
%----------------------
\section{education}
	\begin{entrylist}
    %-----------------
    \entry
    {2007--2009}
    {Masters {\normalfont of Communication Engineering}}
    {National Taiwan University}
    {\emph{Exploiting Online Tags for Music Emotion Classification}} \\
    %-----------------
    \entry
    {2003--2007}
    {Bachelor of Science {\normalfont of Electrical Engineering}}
    {National Taiwan University}
    %-----------------
    \end{entrylist}

%----------------------
%  skills
%----------------------
\section{skill inventory}
    \begin{enumerate}
        \item 2 years experience on C development
        \item 2 years experience on python development
        \item 4 years experience on Matlab development
        \item 1 year experience on Hadoop development
        \item Familiar with developing on Linux and Mac
        \item 4 years experience on research topics including audio/video signal
            processing, music classification, music information retrieval
        \item 1 year experience on applying research techniques to real product
            and cooperating with product developers
    \end{enumerate}


%----------------------
%  experiences
%----------------------
\section{experiences}
\begin{entrylist}
\entry
{2012--Now}
{KKBOX inc.}
{Taipei, Taiwan}
{Research Leader of Research Center} \\
% TODO


    \vspace{-0.1in}
    \begin{tabbing}
        \hspace{0.3in}\= \hspace{4.6in}\= \kill % set up two tab positions
        \underline{\textbf{Research Assistent}} of Pro. Homer H. Chen                          \>\>2007 - 2009 \\
        \underline{\textbf{Reviewer}} of ACMMM '09 and ICIP '08              \>\>2008, 2009 \\
        \underline{\textbf{Research Assistent}} of Spoken Language Group in Academic Sinica     \>\>2007.07 - 2007.09 \\
        \underline{\textbf{Administrative Assisitent}} of Little Giant Chinese Chamber Orchestra    \>\>2005 - 2007 \\
        \underline{\textbf{Leader}} of National Taiwan University Chinese Orchestra              \>\>2005 - 2006 \\
    \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing


\section{Honor}
	\vspace{-0.1in}
	\begin{tabbing}
	\hspace{0.3in}\= \hspace{4.6in}\= \kill
	Third place in the NISSAN Design Award held by Nissan Taiwan \>\>2007 \\
	\> An annual contest for novel electrical equipment or technology on vehicle \\
	\end{tabbing}\vspace{-20pt}

\section{Research Publications}
	\vspace{-0.1in}
	\subsection{Journal}
		\begin{enumerate}[1.~]
			\item \textbf{Y.-C. Lin}, Y.-H. Yang, and H.-H. Chen, 
				``Exploiting online music tags for emotion classification,''
				submitted to ACM Transactions on Multimedia Computing, Communications and Applications (ACM TOMCCAP).
			\item Y.-H. Yang, \textbf{Y.-C. Lin}, Y.-F. Su, and H.-H. Chen, 
				``A regression approach to music emotion recognition,'' 
				IEEE Trans. Audio, Speech and Language Processing (TASLP), 
				vol. 16, no. 2, pp. 448-457, Feb. 2008.
		\end{enumerate}	
	\subsection{Conference}
		\begin{enumerate}[1.~]
			\item Y.-H. Yang, \textbf{Y.-C. Lin}, and H.-H. Chen, 
				``Personalized music emotion retrieval,'' 
				Proc. ACM Int. Conf. Information Retrieval (SIGIR), 
				pp. 748–749, 2009.
			\item Y.-H. Yang, \textbf{Y.-C. Lin}, A. Lee, and H.-H. Chen, 
				``Improving musical concept detection by ordinal regression and context fusion,'' 
				Proc. Int. Conf. Music Information Retrieval (ISMIR), 
				pp. 147–152, 2009.
			\item M.-Y. Su, Y.-H. Yang, \textbf{Y.-C. Lin}, and H.-H. Chen, 
				``An integrated approach to music boundary detection,'' 
				Proc. Int. Conf. Music Information Retrieval (ISMIR), 
				pp. 705–710, 2009.
			\item Y.-H. Yang, \textbf{Y.-C. Lin}, and H.-H. Chen, 
				``Clustering for music search results,''
				Proc. IEEE Int. Conf. Multimedia and Expo (ICME), 
				pp. 874–877, 2009.
			\item \textbf{Y.-C. Lin}, Y.-H. Yang, and H.-H. Chen, 
				``Exploiting genre for music emotion classification,''
				Proc. IEEE Int. Conf. Multimedia and Expo (ICME), 
				pp. 618–621, 2009.
			\item H.-T. Cheng, Y.-H. Yang, \textbf{Y.-C. Lin}, and H.-H. Chen, 
				``Multimodal structure segmentation and analysis of music using audio and textual information,'' 
				Proc. IEEE Int. Symp. Circuits and Systems (ISCAS), 
				pp. 1677–1680, 2009.
			\item Y.-H. Yang, \textbf{Y.-C. Lin}, H.-T. Cheng, and H.-H. Chen, 
				``Mr.Emo: Music retrieval in the emotion plane,'' 
				Proc. ACM Int. Conf. Multimedia (SIGMM), technical demonstration, 
				pp. 1003–1004, 2008.
			\item Y.-H. Yang, \textbf{Y.-C. Lin}, H.-T. Cheng, I.-B. Liao, Yeh-Chin Ho, and H.-H. Chen, 
				``Toward multi-modal music emotion classification,''
				Proc. Pacific-Rim Conf. Multimedia (PCM), 
				pp. 70–79, 2008.
			\item H.-T. Cheng, Y.-H. Yang, \textbf{Y.-C. Lin}, I.-B. Liao, and H.-H. Chen, 
				``Automatic chord recognition for music classification and retrieval,'' 
				Proc. IEEE Int. Conf. Multimedia and Expo (ICME), 
				pp. 1505–1508, 2008.
			\item Y.-H. Yang, Y.-F. Su, \textbf{Y.-C. Lin}, and H.-H. Chen, 
				``Music emotion recognition: The role of individuality,''
				Proc. ACM Int. Workshop on Human-centered Multimedia (ACM HCM), 
				pp. 13–21, 2007.
			\item Y.-H. Yang, \textbf{Y.-C. Lin}, Y.-F Su, and H.-H. Chen, 
				``Music emotion classification: A regression approach,''
				Proc. IEEE Int. Conf. Multimedia and Expo (ICME), 
				pp. 208–211, 2007.
		\end{enumerate}
	\subsection{Patent}
		\begin{enumerate}[1.~]
			\item Y.-C. Lin et al, “A genre-based two-layer structure for music emotion classification,” Taiwan pending.
		\end{enumerate}




\end{document}
